\thetitle

### 2013-09-29 tfpie/response.txt

p5 I think this is the first time the names "BSL" and "Class" are
mentioned.  As far as I know the name BSL is taken from HTDP, and
there does seem to be a few places where it is assumed the reader is
familiar with the content of HTDP. Maybe it would be good to give a
brief summary of the HTDP approach and what these languages are
earlier.

RESPONSE: We clarify what these languages are.

p7 Is this the first mention of "Intermediate Student" language?
Again, maybe in section two where the idea of language levels is
mentioned, maybe it would be good to go into a bit more detail for the
benefit of those who haven't read HTDP.

RESPONSE: We extended section 2 to cover more HTDP background.

@@

p9 Is it possible to include the Racket version alongside this
program? I found it interesting to compare them, and there does seem
to be enough space on the page for it.

RESPONSE: The BSL and Class versions of this program are in figure 1.

### 2013-09-29 tfpie/tfpie.tex
review 2

Thanks to the the preparation in the first half of the course, we can
cover functional OO programming in Java in a just a few lectures.  We
then increase the subset of the language we use to encompass mutation,
loops, and mutable data structures and introduce the underlying design
principles. We present \texttt{ArrayList}s, followed briefly by
arrays. Students use, and then implement, hash tables as well as other
mutable and immutable data structures.  Conventional input and output
are treated only very briefly, as we focus instead on both
fundamentals and exercises making use of real APIs such as hashing
functions or Twitter posting.  Finally, \texttt{while}, \texttt{for},
and for-each loops are presented, following the methodology of \htdc
which connects loops to stylized use of recursive functions with
accumulators, a technique the students now have used for two semesters.

>>>>

Thanks to the the preparation in the first half of the course, we can
cover OO programming in a functional subset of Java in a just a few
lectures.  We then increase the subset of the language we use to
encompass mutation, loops, and mutable data structures and introduce
the underlying design principles. We present \texttt{ArrayList}s,
followed briefly by arrays. Students use, and then implement, hash
tables as well as other mutable and immutable data structures.
Conventional input and output are treated only very briefly, as we
focus instead on both fundamentals and exercises making use of real
APIs such as hashing functions or Twitter posting.  Finally,
\texttt{while}, \texttt{for}, and for-each loops are presented,
following the methodology of \htdc which connects loops to stylized
use of recursive functions with accumulators, a technique the students
now have used for two semesters.
